Title

### 2018-09-20 thesis/paper/paper.tex
Fixed more multiple-atoms writing

\begin{align}
\begin{split}
c = &\text{statement\_EDB}(Q, E, \text{propertyConstant}, X) \wedge{} \\
&\text{statement\_EDB}(S, E, P, V) \wedge \text{unequal}(\text{requiredPropertyConstant}, P)
\end{split} \\
\begin{split}
c = &\text{statement\_EDB}(Q, E, \text{propertyConstant}, X) \wedge{} \\
&\text{statement\_EDB}(S, E, \text{requiredPropertyConstant}, V) \wedge \text{unequal}(\{A\}, V)
\end{split}
\end{align}
\begin{align}
\begin{split}
\text{violation\_statement}&(S, E, \text{propertyConstant}, V) \leftarrow \\
&\text{statement\_EDB}(S, E, \text{propertyConstant}, V) \wedge{} \text{last}(O, I) \wedge{} \\
&\text{require}(O, \text{propertyConstant}, \text{requiredPropertyConstant})
\end{split}
\end{align}

@@

\paragraph{Rules}
The \emph{value requires statement} constraint is syntactically very similar to the previous \emph{item requires statement} constraint. Instead of requiring a statement on the item of a constrained statement, it requires it on the value. Inequality needs to be computed between all properties and all values and the item statement order established. The conjunctions change in the first statement and rule one and two. The final violation rule would be rule three:
\begin{align}
\begin{split}
c = &\text{statement\_EDB}(Q, R, \text{propertyConstant}, I) \wedge{} \\
&\text{statement\_EDB}(S, E, P, V) \wedge \text{unequal}(\text{requiredPropertyConstant}, P)
\end{split}\\
\begin{split}
c = &\text{statement\_EDB}(Q, R, \text{propertyConstant}, I) \wedge{} \\
&\text{statement\_EDB}(S, E, \text{requiredPropertyConstant}, V) \wedge \text{unequal}(\{A\}, V)
\end{split}
\end{align}

>>>>

\begin{align}
\begin{split}
c = &\text{statement\_EDB}(Q, E, \text{propertyConstant}, X) \wedge{} \\
&\text{statement\_EDB}(S, E, P, V) \wedge \text{unequal}(\text{requiredPropertyConstant}, P)
\end{split} \\
\begin{split}
c = &\text{statement\_EDB}(Q, E, \text{propertyConstant}, X) \wedge{} \\
&\text{statement\_EDB}(S, E, \text{requiredPropertyConstant}, V) \wedge {\textstyle\bigwedge}_{a \in A} \text{unequal}(a, V)
\end{split}
\end{align}
\begin{align}
\begin{split}
\text{violation\_statement}&(S, E, \text{propertyConstant}, V) \leftarrow \\
&\text{statement\_EDB}(S, E, \text{propertyConstant}, V) \wedge{} \text{last}(O, I) \wedge{} \\
&\text{require}(O, \text{propertyConstant}, \text{requiredPropertyConstant})
\end{split}
\end{align}

@@

\paragraph{Rules}
The \emph{value requires statement} constraint is syntactically very similar to the previous \emph{item requires statement} constraint. Instead of requiring a statement on the item of a constrained statement, it requires it on the value. Inequality needs to be computed between all properties and all values and the item statement order established. The conjunctions change in the first statement and rule one and two. The final violation rule would be rule three:
\begin{align}
\begin{split}
c = &\text{statement\_EDB}(Q, R, \text{propertyConstant}, I) \wedge{} \\
&\text{statement\_EDB}(S, E, P, V) \wedge \text{unequal}(\text{requiredPropertyConstant}, P)
\end{split}\\
\begin{split}
c = &\text{statement\_EDB}(Q, R, \text{propertyConstant}, I) \wedge{} \\
&\text{statement\_EDB}(S, E, \text{requiredPropertyConstant}, V) \wedge {\textstyle\bigwedge}_{a \in A} \text{unequal}(a, V)
\end{split}
\end{align}
